### 2020-05-17 paper.tex
rxjs-spy

Our work is not the first approach on understanding and improving on the struggles software engineers face when working on RP code, no matter of using RxJS or not. We are going to present academic as well as non-academic efforts which contributed in the field of RP debugging in the past.

@@

>>>>

Our work is not the first approach on understanding and improving on the struggles software engineers have to overcome when working on RP code, either with or without RxJS. We are going to present four of this tools in this section. The list is not meant to be exhaustive. It contains tools we either got to know during our research, because they were mentioned in one of the interviews or we worked with it personally in the past.

@@

\subsection{rxjs-spy}

Software engineers tend to augment their code with additional log trace statements in the situation where they have to track down a problem as we saw earlier. \emph{rxjs-spy} wants to improve on this by introducing the new \mintinline{TypeScript}{tag} operator. Instead of adding log traces at debug-time, ``tagged'' \mintinline{TypeScript}{Observable}s are, hopefully, created right at the moment the \mintinline{TypeScript}{Observable} itself is defined.

\begin{listing}[H]
	\begin{minted}{TypeScript}
		interval(1000).pipe(
		  map(i => i * 2),
		  tag('multiply'),
		  map(i => i - 1)
		).subscribe(console.log);
	\end{minted}
	\caption{Usage of \emph{rxjs-spy} \mintinline{TypeScript}{tag} Operator}
	\label{lst:rxjs-spy-tag}
\end{listing}

Later, \emph{rxjs-spy} can be told to log events (subscribe, emit, error, complete and unsubscribe) of matching tags directly to the console without touching any \mintinline{TypeScript}{Observable} code at all.

\subsection{RxViz}
